Trans-Dimensional Bayesian Inference for Gravitational Lens Substructures

### 2015-10-09 Papers/ms.tex
Paragraph about sersic profiles etc

% For revisions
\newcommand{\revisions}{\color{blue}}

@@

\subsection{The Source}
The surface brightness profile of the source is assumed to be composed of
a sum of a finite number of ``blobs'', or basis functions, in order to
allow some flexibility while incorporating prior information about the
non-negativity of surface brightness, and the spatial correlation expected
in real surface brightness profiles.
For computational speed, we choose the following
functional form for the surface brightness profile
of a single blob centered at the origin:
\begin{eqnarray}
f(x, y) &=& \left\{
\begin{array}{lr}
\frac{2A}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
0, & \textnormal{otherwise}
\end{array}
\right.
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
total flux of the blob (i.e. the integral of the surface brightness over the
entire domain).
These basis functions are inverted paraboloids, which are faster to evaluate
than gaussians, since they do not
contain an exponential function. In addition, the finite support means that
each blob will evaluate to zero over a large fraction of the domain which
confers an additional speed advantage. {\revisions More conventional choices such as
gaussians are possible, as are alternative compact basis functions, perhaps
inspired by the smoothed particle hydrodynamics literature
\citep{2012MNRAS.425.1068D}.}

@@

>>>>

% For revisions
\newcommand{\revisions}{}
\newcommand{\revisionstwo}{\color{blue}}

@@

\subsection{The Source}
The surface brightness profile of the source is assumed to be composed of
a sum of a finite number of ``blobs'', or basis functions, in order to
allow some flexibility while incorporating prior information about the
non-negativity of surface brightness, and the spatial correlation expected
in real surface brightness profiles.
For computational speed, we choose the following
functional form for the surface brightness profile
of a single blob centered at the origin:
\begin{eqnarray}
f(x, y) &=& \left\{
\begin{array}{lr}
\frac{2A}{\pi w^2}\left(1 - \frac{r^2}{w^2}\right), & r \leq w\\
0, & \textnormal{otherwise}
\end{array}
\right.
\end{eqnarray}
where $r = \sqrt{x^2 + y^2}$, $w$ is the width of the blob, and $A$ is the
total flux of the blob (i.e. the integral of the surface brightness over the
entire domain).
These basis functions are inverted paraboloids, which are faster to evaluate
than gaussians, since they do not
contain an exponential function. In addition, the finite support means that
each blob will evaluate to zero over a large fraction of the domain which
confers an additional speed advantage. {\revisions More conventional choices such as
gaussians are possible, as are alternative compact basis functions, perhaps
inspired by the smoothed particle hydrodynamics literature
\citep{2012MNRAS.425.1068D}.} {\revisionstwo Alternative choices, such as Sérsic
profiles, may be more realistic despite their computational cost. This is
especially likely in the case of an early-type source galaxy
\citep[e.g.][]{eels}. Such modifications are possible without great effort
using the {\tt RJObject} library, and once implemented, the marginal likelihood
can be compared across different choices for the source model.}

@@

\bibitem[\protect\citeauthoryear{Auger et al.}{2011}]{eels} 
Auger M.~W., Treu T., Brewer B.~J., Marshall P.~J., 2011, MNRAS, 411, L6
